Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-06-16 analysis/memo2_TAS_reviewers.Rmd
bias disambig and cognizable-class clarification

We suspect the initial reading arose because "bias" has both a statistical meaning and a conventional meaning, and we are using the latter when referring to $b$ as the bias parameter.

@@

By "cognizable" class, we mean the category to which the struck juror belongs that is the possible basis of strike bias. For example, if the set of prospective jurors consists only of Black and White individuals and the focus is on strike bias _against_ Black prospective jurors because of their race, the "cognizable" class is "Black prospective jurors". If, however, the focus is on strike bias against Black female prospective jurors because of their race and gender, the "cognizable" class is "Black female prospective jurors." We used the phrase "cognizable class members subject to strike" instead of "cognizable class jurors", because at the time any strike occurs, (1) no one is actually a juror, because no one has yet been seated onto the jury, and (2) not every prospective juror could have been struck.

>>>>

We have revised the paper in paragraph 2 to expressly distinguish between "bias" as the illegal strike bias (the parameter to be estimated) from "bias" in the statistical sense.  We hope this reduces any confusion.

@@

By "cognizable" class, we mean the social category to which the struck juror belongs that is the possible basis of illegal strike bias. For example, if the set of prospective jurors consists only of Black and White individuals and the focus is on strike bias _against_ Black prospective jurors because of their race, the "cognizable" class is "Black prospective jurors". If, however, the focus is on strike bias against Black female prospective jurors because of their race and gender, the "cognizable" class is "Black female prospective jurors." We used the phrase "cognizable class members subject to strike" instead of "cognizable class jurors", because at the time any strike occurs, (1) no one is actually a juror, because no one has yet been seated onto the jury, and (2) not every prospective juror could have been struck.
